PROTEST

### 2019-09-05 article/main.tex
article: n & si sections

\subsection*{Site index}
\begin{enumerate}
    \item modeled from environmental variables (see "complete model" in code):
    \begin{equation}\label{si}
      si = \alpha + \beta_1 alti + \beta_2 pH +\beta_3 rum +\beta_4 slope +\beta_5 rocheCalc+...+\varepsilon
    \end{equation}
    where $\alpha$ and $\beta_{1-X}$ are parameters to estmiate and $\varepsilon$, the model residuals.
    \item variable selection procedure:
    \begin{enumerate}
        \item remove (one by one) the less significant variables untill all variables are significant
        \item add a quadratic effect on all variables ($\beta_1alti + \beta_1alti^2 + \beta_2slope + \beta_2slope^2...$)
        \item remove (one by one) the variables that became non-significant following the addition of the quadratic effect starting with the least significant ones  untill all variables are significant
\end{enumerate}
    \item assign site index to forest plots: predict $si$ with model and add random noise   [rnorm(nrow(modData), 0, sd(residuals(mod)))]
\end{enumerate}

@@

  \begin{equation}\label{}
    G_{sp} = \frac{n_{sp}\pi Dg_{sp}^2}{4}
  \end{equation}

@@

@@

\begin{equation}\label{one}\tag{1}
  \bullet G_{sp} = \frac{n_{sp}\pi Dg_{sp}^2}{4}
\end{equation}

@@

\begin{equation}\label{}\tag{2}
  \bullet Dg_t^2 = \frac{n_iDg_i^2 + n_jDg_j^2}{n_i + n_j}
\end{equation}

@@

\begin{equation}\label{three}\tag{3}
  \bullet \frac{Dg_i}{Dg_j} = r_{Dg}
\end{equation}

@@

\noindent Using equation \ref{one}, $Dg_t^2$ can be expressed as:

>>>>

\subsection*{Site index}

\noindent We assigned a species-specific site index ($si$) to all forest plots over the study area following a two-step procedure:

\begin{enumerate}
    \item Because not all the variables required to calculate $si$ were available at all locations over the study area, we first modeled the available $si$ at the NFI plots from available environmental variables and LIDAR-derived measures as follows:

    \begin{equation}\label{si}
      si = \alpha + \beta_1 alti + \beta_2 pH +\beta_3 rum +\beta_4 slope +\beta_5 rocheCalc+...+\varepsilon
    \end{equation}

    where $\alpha$ and $\beta_{1-X}$ are parameters to estmiate and $\varepsilon$, the models residuals. We then applied to the models the following variable selection procedure:

        \item We first removed (one by one) the variables whose effect were non-significant starting with the least significant ones untill all variables were significant.

        \item We then added a quadratic effect to all remaining variables (e.g. $\beta_1alti + \beta_1alti^2$).

        \item Finally, we remove (one by one) the variables whose effect became non-significant following the addition of the quadratic effects starting with the least significant ones untill all variables were significant (see the four final species-specific models in SI).

    \item We then calculated $si$ for all forest plots over the study area by adding to the models predictions a random number drawn from the normal distribution $\mathcal{N} (0, \sigma_\varepsilon)$, with $\sigma_\varepsilon$ being the standard deviation of the models residuals.

@@

  \begin{equation}\label{Gsp}
    G_{sp} = \frac{n_{sp}\pi Dg_{sp}^2}{4}
  \end{equation}

@@

\noindent We assigned a number of trees to each species ($n_{sp}$) and on each forest plot by transforming equation \ref{Gsp} as follows:

\begin{equation}\label{}
  n_{sp} = \frac{4G_{sp}}{\pi Dg_{sp}^2}
\end{equation}

\noindent where $G_{sp}$ and $Dg_{sp}$ are the species basal area and quadratic diameter obtained from the procedures detailed above.

@@

\begin{equation}\label{one}\tag{a}
  \bullet G_{sp} = \frac{n_{sp}\pi Dg_{sp}^2}{4}
\end{equation}

@@

\begin{equation}\label{two}\tag{b}
  \bullet Dg_t^2 = \frac{n_iDg_i^2 + n_jDg_j^2}{n_i + n_j}
\end{equation}

@@

\begin{equation}\label{three}\tag{c}
  \bullet \frac{Dg_i}{Dg_j} = r_{Dg}
\end{equation}

@@

\noindent Using equation \ref{one}, $Dg_t^2$ in equation \ref{two} can be expressed as:
